---
title: "Clinic_results"
output: html_document
---
Getting the results by clinic involves taking the weighted mean of every difference $t^2013$ and $t^2014$ for all the dependent variables. The trick here is weighting by number of consults for substantive reasons: the unit of measurement we're interested in is the pap-smear. Thus, each nurse should be counted as the number of patients she sees. 

```{r}
ResultsBYclin<-ddply(ATEbyNurse, .(ExpectedUnitAtTMT),   
                       function(x) data.frame(Said1or2Lab0_Said1_diff2014=weighted.mean(x$Said1or2Lab0_Said1_diff2014, x$numcons2014,na.rm=TRUE),
                                              Said0LabNo_Toc_diff2014=weighted.mean(x$Said0LabNo_Toc_diff2014, x$numcons2014,na.rm=TRUE),
                                              Said9LabNo_numcons_diff2014=weighted.mean(x$Said9LabNo_numcons_diff2014, x$numcons2014,na.rm=TRUE),
                                              Grade1_diff2014=weighted.mean(x$Grade1_diff2014, x$numcons2014,na.rm=TRUE),
                                              Said1or2Lab0_Said1_diff14_13=weighted.mean(x$Said1or2Lab0_Said1_diff13_14, x$numcons2014,na.rm=TRUE),
                                              Said0LabNo_Toc_diff14_13=weighted.mean(x$Said0LabNo_Toc_diff13_14, x$numcons2014,na.rm=TRUE),
                                              Said9LabNo_numcons_diff14_13=weighted.mean(x$Said9LabNo_numcons_diff13_14, x$numcons2014,na.rm=TRUE),
                                              Grade1_diff14_13=weighted.mean(x$Grade1_diff13_14, x$numcons2014,na.rm=TRUE),
                                              numcons2014=sum(x$numcons2014,na.rm=TRUE),
                                              numnurse2014=length(unique(x$matricula))))

```

Now I merge this with other data from clinics (from TMTstats). 

```{r}
ClinResults<-merge(TMTstats,ResultsBYclin,by.x="unidadmedica",by.y="ExpectedUnitAtTMT")
```

# You can also embed plots, for example:
# 
# ```{r, echo=FALSE}
# plot(cars)
# 
# Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.